Trending assessment for nowcasts, measurements, and forecasts

### 2024-02-27 sections/04-application.tex
Update Covid nowcast analysis

\begin{table}
    \centering
    \missingfigure{TABLE}
    \caption{Trending ratios for the models with and without exclusion areas. The exclusion areas are rectangles centered on the zero points with width and height ... . The ratios are calculated for the lags 1, 7, and 14 days.}
    \label{tab:app-covid-ratios}
\end{table}

>>>>

\begin{table}
    \centering
    \tiny
    \input{plots/covid_nowcast/30_trending_ratios_lag_7.tex}
    \caption{Trending ratio $\acc$, positive trending ratio $\accp$, and negative trending ratio $\accm$ for the models with and without exclusion areas for the lag 7 days. The exclusion areas are rectangles centered on the zero points with width and height of 10\% of the quantile of the absolute values of nowcast and true values. }
    \label{tab:app-covid-trending-ratios-lag-7}
\end{table}

### 2024-02-27 sections/55-appendix-application-covid.tex
Update Covid nowcast analysis

\begin{figure}
    \centering
    \begin{subfigure}[t]{.31\textwidth}
        \missingfigure{KDE for true and nowcasts of lag 1.}
        \caption{\ac{kde} for true values and nowcasts of lag 1.}
    \end{subfigure}\hspace{0.01\textwidth}
    \begin{subfigure}[t]{.31\textwidth}
        \missingfigure{KDE for true and nowcasts of lag 7.}
        \caption{\ac{kde} for true values and nowcasts of lag 7.}
    \end{subfigure}\hspace{0.01\textwidth}
    \begin{subfigure}[t]{.31\textwidth}
        \missingfigure{KDE for true and nowcasts of lag 14.}
        \caption{\ac{kde} for true values and nowcasts of lag 14.}
    \end{subfigure}
    \caption{\Ac{kde} for true values and nowcasts of lags 1, 7, and 14 to assess the distribution of values. \hl{AUSWERTUNG; 10 \% der Werte liegen innerhalb von ... um den Ursprung.}}
    \label{fig:app-covid-kde}
\end{figure}

\begin{table}
    \centering
    \begin{tabular}{l X}
        \toprule
        Abbreviation & Nowcasting hub key \\
        \midrule
        EPI & Epiforecasts-independent \\
        ILM & ILM-prop \\
        KIT & KIT-simple\_nowcast \\
        LMU & LMU\_StaBLab-GAM\_nowcast \\
        RIVM & RIVM-KEW \\
        RKI & RKI-weekly\_report \\
        SU & SU-hier\_bayes \\
        SZ & SZ-hosp\_nowcast\\
        ENS-MEAN & NowcastHub-MeanEnsemble\\
        ENS-MED & NowcastHub-MedianEnsemble\\
        \bottomrule
    \end{tabular}
    \caption{Matching of the abbreviation to the key in the nowcasting hub .Information on the models and references are listed in \textcite[][Table 1]{Wolffram2023}.}
    \label{tab:app-covid-models}
\end{table}

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[t]{.48\textwidth}
        \includegraphics{plots/covid_nowcast/20_kde_lag_1}
        \caption{\ac{kde} for true values and nowcasts of lag 1.}
    \end{subfigure}\hspace{0.01\textwidth}
    \begin{subfigure}[t]{.48\textwidth}
        \includegraphics{plots/covid_nowcast/20_kde_lag_7}
        \caption{\ac{kde} for true values and nowcasts of lag 7.}
    \end{subfigure}\hspace{0.01\textwidth}
    \begin{subfigure}[t]{.48\textwidth}
        \includegraphics{plots/covid_nowcast/20_kde_lag_14}
        \caption{\ac{kde} for true values and nowcasts of lag 14.}
    \end{subfigure}
    \caption{\Ac{kde} for true values and nowcasts of lags 1, 7, and 14 to assess the distribution of values. \hl{AUSWERTUNG}. Exclusion areas based on the 10\%  quantile of absolute values are listed in Table~\ref{tab:app-covid-marginals}.}
    \label{fig:app-covid-kde}
\end{figure}

\begin{table}
    \centering
    \begin{tabular}{l l}
        \toprule
        Abbreviation & Nowcasting hub key \\
        \midrule
        EPI & Epiforecasts-independent \\
        ILM & ILM-prop \\
        KIT & KIT-simple\_nowcast \\
        LMU & LMU\_StaBLab-GAM\_nowcast \\
        RIVM & RIVM-KEW \\
        RKI & RKI-weekly\_report \\
        SU & SU-hier\_bayes \\
        SZ & SZ-hosp\_nowcast\\
        ENS-MEAN & NowcastHub-MeanEnsemble\\
        ENS-MED & NowcastHub-MedianEnsemble\\
        \bottomrule
    \end{tabular}
    \caption{Matching of the abbreviation to the key in the nowcasting hub. Information on the models and references is listed in \textcite[][Table 1]{Wolffram2023}.}
    \label{tab:app-covid-models}
\end{table}

\begin{table}
    \centering
    \input{plots/covid_nowcast/10_marginal_analysis}
    \caption{Analysis of the nowcast and true differences for the lags 1, 7, and 14 days.}
    \label{tab:app-covid-marginals}
\end{table}

\begin{table}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \input{plots/covid_nowcast/30_trending_ratios_lag_1.tex}
    \caption{1 day.}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \input{plots/covid_nowcast/30_trending_ratios_lag_1.tex}
        \caption{14 days.}
    \end{subfigure}
    \caption{Trending ratio $\acc$, positive trending ratio $\accp$, and negative trending ratio $\accm$ for the models with and without exclusion areas for the lag 1 and 14 days. The exclusion areas are rectangles centered on the zero points with width and height of 10\% of the quantile of the absolute values of nowcast and true values. }
    \label{tab:app-covid-trending-ratios-lag-1-14}
\end{table}

\begin{figure}
\centering
\begin{subfigure}[t]{0.23\textwidth}
    \includegraphics{plots/covid_nowcast/30_ENS-MEAN_4q_lag_1}
    \caption{ENS-Mean, lag 1 day}\label{fig:app-covid-4q-ens-mean-1}
\end{subfigure}\hspace{0.01\textwidth}%
\begin{subfigure}[t]{0.23\textwidth}
    \includegraphics{plots/covid_nowcast/30_ILM_4q_lag_1}
    \caption{ILM, lag 1 day}\label{fig:app-covid-4q-ilm-1}
\end{subfigure}\hspace{0.01\textwidth}%
\begin{subfigure}[t]{0.23\textwidth}
    \includegraphics{plots/covid_nowcast/30_RIVM_4q_lag_1}
    \caption{RIVM, lag 1 day}\label{fig:app-covid-4q-rivm-1}
\end{subfigure}\hspace{0.01\textwidth}%
\begin{subfigure}[t]{0.23\textwidth}
    \includegraphics{plots/covid_nowcast/30_RKI_4q_lag_1}
    \caption{RKI, lag 1 day}\label{fig:app-covid-4q-rki-1}
\end{subfigure}
% lag 7
\begin{subfigure}[t]{0.23\textwidth}
    \includegraphics{plots/covid_nowcast/30_ENS-MEAN_4q_lag_7}
    \caption{ENS-Mean, lag 7 days}\label{fig:app-covid-4q-ens-mean-7}
\end{subfigure}\hspace{0.01\textwidth}%
\begin{subfigure}[t]{0.23\textwidth}
    \includegraphics{plots/covid_nowcast/30_ILM_4q_lag_7}
    \caption{ILM, lag 7 days}\label{fig:app-covid-4q-ilm-7}
\end{subfigure}\hspace{0.01\textwidth}%
\begin{subfigure}[t]{0.23\textwidth}
    \includegraphics{plots/covid_nowcast/30_RIVM_4q_lag_7}
    \caption{RIVM, lag 7 days}\label{fig:app-covid-4q-rivm-7}
\end{subfigure}\hspace{0.01\textwidth}%
\begin{subfigure}[t]{0.23\textwidth}
    \includegraphics{plots/covid_nowcast/30_RKI_4q_lag_7}
    \caption{RKI, lag 7 days}\label{fig:app-covid-4q-rki-7}
\end{subfigure}
% lag 14
\begin{subfigure}[t]{0.23\textwidth}%
    \includegraphics{plots/covid_nowcast/30_ENS-MEAN_4q_lag_14}
    \caption{ENS-Mean, lag 14 days}\label{fig:app-covid-4q-ens-mean-14}
\end{subfigure}\hspace{0.01\textwidth}
\begin{subfigure}[t]{0.23\textwidth}%
    \includegraphics{plots/covid_nowcast/30_ILM_4q_lag_14}
    \caption{ILM, lag 14 days}\label{fig:app-covid-4q-ilm-14}
\end{subfigure}\hspace{0.01\textwidth}
\begin{subfigure}[t]{0.23\textwidth}%
    \includegraphics{plots/covid_nowcast/30_RIVM_4q_lag_14}
    \caption{RIVM, lag 14 days}\label{fig:app-covid-4q-rivm-14}
\end{subfigure}\hspace{0.01\textwidth}%
\begin{subfigure}[t]{0.23\textwidth}
    \includegraphics{plots/covid_nowcast/30_RKI_4q_lag_14}
    \caption{RKI, lag 14 days}\label{fig:app-covid-4q-rki-14}
\end{subfigure}%
\caption{Four-quadrant plots for the models ILM, RIVM, RKI, and ENS-MEAN and the lags of one, seven, and 14 days. }
\label{fig:app-covid-4q}
\end{figure}
